Data preparation for employee category analysis

### 2023-05-24 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Corrected calculation of whole team teleworking

Identify employees who telework and collect `person_id`, `dates`, `location`, and `supervisor_e_mail_address`.

```{r}
prep_a <-
  cohort_panel %>% 
  filter(daily_status_imputed == "Teleworking") %>%
  select(person_id, date, location, supervisor_e_mail_address) %>%
  distinct()
```

@@

@@

```{r}
prep_c <- 
  prep_b %>% 
  group_by(person_id,date,supervisor_e_mail_address) %>% 
  summarise(telework_team_members = n_distinct(person_id_joined)) %>% 
  ungroup()
```

@@

@@

```{r}
prep_e <- 
  prep_c %>% 
  left_join(prep_d) %>% 
  filter(telework_team_members == team_size)
```

>>>>

Identify employees who telework and collect `person_id`, `dates`, and `supervisor_e_mail_address`.

```{r}
prep_a <-
  cohort_panel %>% 
  filter(daily_status_imputed == "Teleworking") %>%
  select(person_id, date, supervisor_e_mail_address) %>%
  distinct()
```

@@

Count number of distinct `person_id`s by `dates`, and `supervisor_e_mail_address`.

```{r}
prep_b <- 
  prep_a %>% 
  group_by(date, supervisor_e_mail_address) %>%
  summarise(telework_team_members = n_distinct(person_id)) %>% 
  ungroup()
```

@@

```{r}
prep_c <- 
  cohort_panel %>% 
  group_by(date,supervisor_e_mail_address) %>% 
  summarise(team_size = n_distinct(person_id)) %>% 
  ungroup()
```

@@

```{r}
prep_d <- 
  prep_b %>% 
  left_join(prep_c) %>% 
  filter(telework_team_members == team_size)
```

@@

Inner join `cohort_panel` to `prep_d` to only capture employees on days where the whole team is remote.

```{r}
prep_e <- 
  cohort_panel %>% 
  select(person_id,supervisor_e_mail_address,date) %>% 
  distinct() %>% 
  inner_join(prep_d)
```
